Keyphrase Extraction from User Generated Contents on Medical Domain

### 2017-05-24 paper.tex
nambah dikit

It can be seen on the example that keyphrases can be a word, phrase, or even clause. Furthermore, there are many grammatical errors and abbreviation, such as \texttt{"sy"} for the replacement of the word \texttt{"saya (I)"}. It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of medical entity categories. Thus, extracting keyphrase for getting patient needs is not a trivial task.

@@

\subsection{Results}
\begin{table}
	\caption{Model Scenario Results}
	\label{tab:model_scenario}
	\begin{tabular}{lccc}
		\toprule
		Models&Precision&Recall&F-Measure\\
		\midrule
		RAKE & 43.24\% & 68.19\% & 52.90\% \\

@@

\subsection{Analysis}
We performed an analysis to the aforementioned model, the result shown there are several errors. Some of the error are uncompleted keyphrases. For example, "pusing pada (headache on)", "obat untuk (medicine for)". Our model also failed to capture complex medicine name and disease. This is due to our small data set and not all medicine and disease are captured in our medical knowledge base or medical entities. Moreover, there are also special case that our model failed to handle. For example, "penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)", the keyphrase need to be captured as a whole because "sore throat" have a connection with the word "treatment". But our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
\iffalse
We also ablate our model by removing our features one by one. As we can see in Table \ref{tab:ablation}, F1 score always dropped when we removed one feature. Hence, we can say that all of our features are effective for this task.
 \begin{table}
	\caption{Average Change in Performance When Removing Each Feature}
	\label{tab:ablation}
	\begin{tabular}{cccc}
		\toprule
		Removed Features&Precision&Recall&F-Measure\\
		\midrule
            We & -4.08 & -18.34 & -12.84 \\
            Md & -8.35 & +0.24 & -3.84 \\
            Wl & -8.65 & +0.49 & -3.87 \\
            Wp & -9.77 & +2.44 & -3.5 \\
            Pt & -4.33 & -0.98 & -2.52 \\
            Wa & -5.57 & -1.96 & -3.62 \\
            Wi & -0.32 & -0.49 & -0.42 \\
            Me & -4.63 & +0.49 & -1.89 \\
            Ws & -7.62 & -2.2 & -4.73 \\
		\bottomrule
	\end{tabular}
\end{table}
\fi
\section{Conclusion}
We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain. Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text. Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm. We also proposed a new layer for weighting our features. Furthermore, Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing. Although our model outperforms baseline methods for keyphrase extraction, further improvements are needed.

>>>>

It can be seen on the example that keyphrases can be a word, phrase, or even clause. Furthermore, there are many grammatical errors and abbreviation, such as \texttt{"sy"} for the replacement of the word \texttt{"saya (I)"}. It is also worth to note that keyphrase \texttt{"diet mayo (mayo diet)"} is not part of any medical entity categories. Thus, we argue that extracting keyphrase from user-generated content especially on medical domain is not a trivial task.

@@

\subsection{Results and Analyisis}
\begin{table}
	\caption{Model Scenario Results}
	\label{tab:model_scenario}
	\begin{tabular}{lccc}
		\toprule
		Models&Precision&Recall&F-Measure\\
		\midrule
		RAKE & 43.24\% & 68.19\% & 52.90\% \\

@@

We performed an analysis to the aforementioned model, the result shown there are several errors. Some of the error are uncompleted keyphrases. For example, "pusing pada (headache on)", "obat untuk (medicine for)". Our model also failed to capture complex medicine name and disease. This is due to our small data set and not all medicine and disease are captured in our medical knowledge base or medical entities. Moreover, there are also special case that our model failed to handle. For example, "penyembuhan untuk sakit kepala dan tenggorokan (treatment for headache and sore throat)", the keyphrase need to be captured as a whole because "sore throat" have a connection with the word "treatment". But our model failed to capture that connection and extracted "treatment for headache" and "sore throat" separately instead.
\iffalse
We also ablate our model by removing our features one by one. As we can see in Table \ref{tab:ablation}, F1 score always dropped when we removed one feature. Hence, we can say that all of our features are effective for this task.
 \begin{table}
	\caption{Average Change in Performance When Removing Each Feature}
	\label{tab:ablation}
	\begin{tabular}{cccc}
		\toprule
		Removed Features&Precision&Recall&F-Measure\\
		\midrule
            We & -4.08 & -18.34 & -12.84 \\
            Md & -8.35 & +0.24 & -3.84 \\
            Wl & -8.65 & +0.49 & -3.87 \\
            Wp & -9.77 & +2.44 & -3.5 \\
            Pt & -4.33 & -0.98 & -2.52 \\
            Wa & -5.57 & -1.96 & -3.62 \\
            Wi & -0.32 & -0.49 & -0.42 \\
            Me & -4.63 & +0.49 & -1.89 \\
            Ws & -7.62 & -2.2 & -4.73 \\
		\bottomrule
	\end{tabular}
\end{table}
\fi
\section{Conclusion}
We have proposed a model to address the task of keyphrase extraction on Indonesian user-generated medical domain. Extracting information patient intentions and needs on user-generated medical contents is not a trivial task due to the fact that the content is usually short, contain many medical terms, and written in an unstructured format, as opposed to formal text. Our model is based on sequence labeling task that employs deep learning approach using convolutional neural networks and bi-directional lstm. We also proposed a new layer for weighting our features. Furthermore, Several handcrafted features were proposed, including word importance to detect important word in a document and word stickiness for handling unstructured writing. Although our model outperforms baseline methods for keyphrase extraction, further improvements are needed.
